A Poll-of-Polls Forecast for the 2024 U.S. Presidential Election: Analysis of Support Trends for Harris Accounting for Pollster and State Disparities

### 2024-11-01 paper/paper.qmd
fix for tables/figures spilling out of the page

The paper is structured as follows. Initially, @sec-data and @sec-model explores the data and methodology used, including filtering and modeling techniques applied to the polling data. Following that, @sec-results presents the results from the linear and Bayesian models, while the next section @sec-discussion discusses the broader implications of these findings. Finally, the paper concludes with remarks on future directions for research and applications of these models [@sec-discussion].

@@

We use the statistical programming language R [@citeR] to analyze US presidential polling data from FiveThirtyEight [@fivethirtyeight2024], focusing on support for Kamala Harris (Note that the data was last updated on 30 Oct. 2024). The dataset includes a wide range of poll results from various national and state-level polls, with key variables such as pollster, sample size, percentage of support for Harris, and end date of the poll. Following the guidance of @tellingstories, we compiled the results of each opinion poll over a period of time and compared them taking into account the methodological peculiarities of polling by pollsters and geographical scope of the conducted polls.

@@

(Data last updated on 30 Oct 2024.) - [!!! MODIFY AT FINAL !!!]

@@

[!!! MODIFY OBSV. NUMBERS AFTER DATA UPDATES !!!] - ERASE AT FINAL

The original dataset sourced from FiveThirtyEight [@fivethirtyeight2024] aggregates a wide range of poll results (16817 observations, based on dataset available at Oct 30). The polls conducted by various polling organizations capture voter preferences by taking a representative sample of the electorate and asking for the voters' candidate of choice. Surveys were conducted at the state and national levels, providing the wide perspective on public feelings across the country.

@@

```{r}
#| label: tbl-pctraw1
#| tbl-cap: Summary statistics for the proportion(%) of support that candidates received in the poll
#| echo: false

@@

```
```{r}
#| label: fig-pct2
#| fig-cap: Distribution of the proportion(%) of support that candidates received in the poll
#| echo: false

# Plot the distribution of 'pct' using a histogram
ggplot(raw_elections_data, aes(x = pct)) +
  geom_histogram(binwidth = 5, fill = "blue", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Percentage of Support (pct)",
       y = "Frequency")

```
```{r}
#| label: tbl-pctfilter1
#| tbl-cap: Summary statistics for the proportion(%) of support that Harris received in high-quality polls
#| echo: false

@@

```
```{r}
#| label: fig-pctfilter2
#| fig-cap: Distribution of the proportion(%) of support that Harris received in high-quality polls
#| echo: false

# Plot the distribution of 'pct' using a histogram
ggplot(harris_data, aes(x = pct)) +
  geom_histogram(binwidth = 5, fill = "blue", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Percentage of Support (pct)",
       y = "Frequency")

@@

[!!! MODIFY DATE RANGE AFTER DATA UPDATES !!!] - ERASE AT FINAL

The 'end_date' variable representing the time the poll was concluded was put into account to keep track of how support for a candidate changes in time. The reported end dates in the original dataset [@fivethirtyeight2024] ranges from 27 April, 2021 to 29 October, 2024 (@tbl-date). @fig-date shows that the polling data is more concentrated on survey results conducted in the recent period.

```{r}
#| label: tbl-date
#| tbl-cap: Summary statistics for the date the poll was concluded
#| echo: false

@@

```
```{r}
#| label: fig-date
#| fig-cap: Distribution of the date the poll was concluded
#| echo: false

@@

[!!! MODIFY DATE RANGE AFTER DATA UPDATES !!!] - ERASE AT FINAL

When filtering the data, not only pollster quality and candidate type but also the date variable was considered. The filtered data contains only the polling data after the declaration of Harris. So, the date variable for filtered data ranges from 23 July, 2024 to 29 October, 2024 (@tbl-date2). @fig-date2 shows that overall, polling is conducted regularly but intensifies around specific dates.

```{r}
#| label: tbl-date2
#| tbl-cap: Summary statistics for the date the high-quality polls for Harris was concluded
#| echo: false

@@

```{r}
#| label: fig-date2
#| fig-cap: Distribution of the date the high-quality polls for Harris was concluded
#| echo: false

@@

```{r}
#| label: tbl-predictors1
#| tbl-cap: Number of distinct polling organizations and US states where the poll was conducted
#| echo: false

@@

```{r}
#| label: tbl-predictors2
#| tbl-cap: Number of distinct high-quality polling organizations and US states where more than 60 polls for Harris were conducted
#| echo: false

@@

The distribution of polling counts for different pollsters in @fig-pollster suggests that the analysis data is dominated by a few pollsters, particularly Siena/NYT. Depending on their polling methodology, the general results may have potential biases. A detailed analysis of the polling methodology and possible errors of the organization will be covered in @sec-data-details.

```{r}
#| label: fig-pollster
#| fig-cap: Distribution of polling organizations where high-quality polls for Harris were conducted
#| echo: false

@@

```{r}
#| label: fig-state
#| fig-cap: Distribution of US states where the more than 60 polls for Harris were conducted
#| echo: false

@@

```{r}
#| label: tbl-pollscore
#| tbl-cap: Summary statistics for the reliability scores of pollsters
#| echo: false

@@

```{r}
#| label: fig-pollscore
#| fig-cap: Distribution of the reliability scores of pollsters
#| echo: false

@@

```{r}
#| label: tbl-pollscore2
#| tbl-cap: Summary statistics for the reliability scores of high-quality pollsters used for analysis
#| echo: false

@@

```{r}
#| label: fig-pollscore2
#| fig-cap: Distribution of the reliability scores of high-quality pollsters used for analysis
#| echo: false

@@

## Correlation Between Predictor Variables

@@

```{r}
#| label: fig-correlation1
#| fig-cap: "Polling concentration over time by state *Note:* Strategic focus of polling is directed in battleground states such as Pennsylvania and Ohio in September 15, 2024"
#| echo: false

@@

# Plot a heatmap of polling activity by state and week
ggplot(poll_time_state_2, aes(x = week, y = state, fill = total_polls)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey90") +
  labs(x = "Week",
       y = "State",
       fill = "Total Polls") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r}
#| label: fig-correlation2
#| fig-cap: "Polling concentration over time by pollster *Note:* Concentrated polling efforts of Siena/NYT in the first half of September, 2024 show temporal bias and potential overemphasizing of their polling methodologies around key election events."
#| echo: false

@@

# Plot a heatmap of polling activity by state and week
ggplot(poll_time_pollster, aes(x = week, y = pollster, fill = total_polls)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey90") +
  labs(x = "Week",
       y = "Pollster",
       fill = "Total Polls") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r}
#| label: fig-correlation3
#| fig-cap: "Polling activity by pollster and state *Note:* Siena/NYT has strongest state-level polling coverage in key battleground states"
#| echo: false

@@

# Step 2: Plot the faceted map using plot_usmap
plot_usmap(data = pollster_state_data, values = "total_polls", regions = "states") +
  facet_wrap(~ pollster, ncol = 2) +  # Create a map for each pollster
  scale_fill_distiller(palette = "Blues", direction = 1, na.value = "gray90") +  # Use blue color palette
  labs(fill = "Total Polls") +
  theme_void() +  # Remove axes and gridlines
  theme(strip.text = element_text(size = 12))  # Customize facet labels

@@

The goal of our modelling strategy is to estimate Kamala Harris's support percentage in the 2024 US election polls, accounting for potential variations over time, as well as across different pollsters and states. The model balances complexity with interpretability, incorporating both linear and Bayesian frameworks to capture patterns in the data. Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

## Results from the relation between the prediction variable and outcome variable of the analysis data

@@

```{r}
#| label: fig-resultplot1
#| fig-cap: "Polling votes for Harris over time *Note:* The date starts from after Harris officially announced her campaign for 2024 U.S. presidential election on July 21, 2024."
#| echo: false
#| warning: false

@@

When accounting for the pollster difference, @fig-resultplot2 and @fig-resultplot3 show variations in Harris' support levels that are obscured in the aggregated view of @fig-resultplot1. Siena/NYT (pink) shows relatively stable polling results for Harris, with fewer extreme values and a slight downward trend in October. On the other hand, Emerson (greem) shows more fluctuation throughout the period with a wider spread of polling values.

```{r}
#| label: fig-resultplot2
#| fig-cap: "Polling votes for Harris over time by pollster *Note:* The date starts from after Harris officially announced her campaign for 2024 U.S. presidential election on July 21, 2024. Only filtered pollsters with high-quality polling questions are shown in the following."
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-resultplot3
#| fig-cap: "Polling votes for Harris over time by pollster (facets) *Note:* The date starts from after Harris officially announced her campaign for 2024 U.S. presidential election on July 21, 2024. Only filtered pollsters with high-quality polling questions are shown in the following."
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-resultplot4
#| fig-cap: "Polling votes for Harris over time by state *Note:* The date starts from after Harris officially announced her campaign for 2024 U.S. presidential election on July 21, 2024. Only filtered pollsters with high-quality polling questions are shown in the following."
#| echo: false
# Color by pollster
#| warning: false

base_plot +
  geom_point(aes(color = state)) +
  geom_smooth() + 
  theme(legend.position = "bottom")
```

```{r}
#| label: fig-resultplot5
#| fig-cap: "Polling votes for Harris over time by state (facets) *Note:* The date starts from after Harris officially announced her campaign for 2024 U.S. presidential election on July 21, 2024. Only filtered pollsters with high-quality polling questions are shown in the following."
#| echo: false
#| warning: false

@@

Prediction results derived from our model frameworks are summarized in @tbl-modelresults1 and @tbl-modelresults2. In the linear models (@tbl-modelresults1)
, higher $R^2$ and lower WAIC, RMSE values in the second column show that the inclusion of pollster effects improves accuracy and reliability of the prediction model. In the Bayesian models (@tbl-modelresults2), higher Log-Likelihood and lower ELPD, WAIC values in the fourth column shows that including both pollster and state effects enhances model performance.

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults1
#| tbl-cap: "Linear models of support percentages for Harris based on date and pollster"
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults2
#| tbl-cap: "Bayesian models of support percentages for Harris based on pollster and state"
#| warning: false

@@

While our model provides a foundation to understand Harris' polling support, further refinements are necessary to enhance its accuracy and applicability. For instance, future studies could focus on the incorporation of voter demographics, such as age, gender, and education. Showing which segments of the population are driving changes in support, this can give further explanation to how certain policies or campaign events of candidates affect overall support for a candidate. In addition, interaction terms between pollster and state can be included in the model, considering that some states might receive disproportionately more attention from certain pollsters as shown in @fig-correlation3. This can give further explanation to how pollsters and regional dynamics affect overall support for a candidate.

This study has its constraints in that sampling error and systematic biases inevitably occur in the process of measuring social phenomenon with data. In particular, due to the nature of polling surveys, non-responses or misunderstanding of the survey questions result in missing data or outliers. Considering the possibility of prediction errors, we should take caution in interpreting the analysis and prediction results. By conducting more in-depth research of the domain knowledge and constructing appropriate variables to put into account, it would help derive accurate conclusions rather than just acknowledging the numbers given itself.

@@

# Appendix

# Additional data details {#sec-data-details}

## Pollster Methodology Overview and Evaluation

@@

## Idealized Methodolgy

@@

## Idealized Survey

The proposed survey questionnarie design is provided in the following link:
https://forms.gle/zQ8iJyPk3HhJYrKd9.

::: {.layout}
## Survey Demo

@@

# Model details {#sec-model-details}

## Posterior predictive check

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheck
#| layout-ncol: 2
#| fig-cap: "Examining how the Bayesian model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check"]

@@

## Diagnostics

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

>>>>

The paper is structured as follows. Initially, @sec-data and @sec-model explores the data and methodology used, including filtering and modeling techniques applied to the polling data. Following that, @sec-results presents the results from the linear and Bayesian models, while the next section @sec-discussion discusses the broader implications of these findings. Finally, @sec-appendix provides an in-depth overview of the pollster methodology, outline an idealized survey methodology, and detail the modeling techniques employed in our analysis.

@@

We use the statistical programming language R [@citeR] to analyze US presidential polling data from FiveThirtyEight [@fivethirtyeight2024], focusing on support for Kamala Harris. The dataset, last updated on 30 October 2024, includes a wide range of poll results from various national and state-level polls, with key variables such as pollster, sample size, percentage of support for Harris, and end date of the poll. Following the guidance of @tellingstories, we compiled the results of each opinion poll over a period of time and compared them taking into account the methodological peculiarities of polling by pollsters and geographical scope of the conducted polls.

@@

@@

The original dataset sourced from FiveThirtyEight [@fivethirtyeight2024] aggregates a wide range of poll results, showing 16817 observations based on dataset available at October 30. The polls conducted by various polling organizations capture voter preferences by taking a representative sample of the electorate and asking for the voters' candidate of choice. Surveys were conducted at the state and national levels, providing the wide perspective on public feelings across the country.

@@

```{r}
#| label: tbl-pctraw1
#| tbl-cap: Summary statistics for the proportion(%) of support that candidates received in the poll
#| echo: false
#| tbl-align: center
#| tbl-width: 80%

@@

```
```{r}
#| label: fig-pct2
#| fig-cap: Distribution of the proportion(%) of support that candidates received in the poll
#| echo: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

# Plot the distribution of 'pct' using a histogram
ggplot(raw_elections_data, aes(x = pct)) +
  geom_histogram(binwidth = 5, fill = "blue", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Percentage of Support (pct)",
       y = "Count")

```
```{r}
#| label: tbl-pctfilter1
#| tbl-cap: Summary statistics for the proportion(%) of support that Harris received in high-quality polls
#| echo: false
#| tbl-align: center
#| tbl-width: 80%

@@

```{r}
#| label: fig-pctfilter2
#| fig-cap: Distribution of the proportion(%) of support that Harris received in high-quality polls
#| echo: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

# Plot the distribution of 'pct' using a histogram
ggplot(harris_data, aes(x = pct)) +
  geom_histogram(binwidth = 5, fill = "blue", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Percentage of Support (pct)",
       y = "Count")

@@

The 'end_date' variable representing the time the poll was concluded was put into account to keep track of how support for a candidate changes in time. The reported end dates in the original dataset [@fivethirtyeight2024] ranges from 7 April, 2021 to 29 October, 2024 (@tbl-date). @fig-date shows that the polling data is more concentrated on survey results conducted in the recent period.

```{r}
#| label: tbl-date
#| tbl-cap: Summary statistics for the date that the poll was concluded
#| echo: false
#| tbl-align: center
#| tbl-width: 80%

@@

```{r}
#| label: fig-date
#| fig-cap: Distribution of the date that the poll was concluded
#| echo: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

@@

When filtering the data, not only pollster quality and candidate type but also the date variable was considered. The filtered data contains only the polling data after the declaration of Harris. So, the date variable for filtered data in @tbl-date2 ranges from 23 July, 2024 to 29 October, 2024. @fig-date2 shows that overall, polling is conducted regularly but intensifies around specific dates.

```{r}
#| label: tbl-date2
#| tbl-cap: Summary statistics for the date that high-quality polls for Harris was concluded
#| echo: false
#| tbl-align: center
#| tbl-width: 80%

@@

```{r}
#| label: fig-date2
#| fig-cap: Distribution of the date that high-quality polls for Harris was concluded
#| echo: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

@@

```{r}
#| label: tbl-predictors1
#| tbl-cap: Number of distinct polling organizations and US states where the poll was conducted
#| echo: false
#| tbl-align: center
#| tbl-width: 80%

@@

```{r}
#| label: tbl-predictors2
#| tbl-cap: Number of distinct high-quality polling organizations and US states where more than 60 polls for Harris were conducted
#| echo: false
#| tbl-align: center
#| tbl-width: 80%

@@

The distribution of polling counts for different pollsters in @fig-pollster suggests that the analysis data is dominated by a few pollsters, particularly Siena/NYT. Depending on their polling methodology, the general results may have potential biases. A detailed analysis of the polling methodology and possible errors of the organization will be covered in @sec-appendix.

```{r}
#| label: fig-pollster
#| fig-cap: Distribution of polling organizations where high-quality polls for Harris were conducted
#| echo: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

@@

```{r}
#| label: fig-state
#| fig-cap: Distribution of US states where the more than 60 polls for Harris were conducted
#| echo: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

@@

```{r}
#| label: tbl-pollscore
#| tbl-cap: Summary statistics for the reliability scores of pollsters
#| echo: false
#| tbl-align: center
#| tbl-width: 80%

@@

```{r}
#| label: fig-pollscore
#| fig-cap: Distribution of the reliability scores of pollsters
#| echo: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

@@

```{r}
#| label: tbl-pollscore2
#| tbl-cap: Summary statistics for the reliability scores of high-quality pollsters in the analysis data
#| echo: false
#| tbl-align: center
#| tbl-width: 80%

@@

```{r}
#| label: fig-pollscore2
#| fig-cap: Distribution of the reliability scores of high-quality pollsters in the analysis data
#| echo: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

@@

## Correlation between predictor variables

@@

```{r}
#| label: fig-correlation1
#| fig-cap: "Polling concentration over time by state (*Note:* Strategic focus of polling is directed in battleground states such as Pennsylvania and Ohio in September 15, 2024)"
#| echo: false
#| fig-align: center
#| page-break-after: true

@@

# Plot a heatmap of polling activity by state and week
ggplot(poll_time_state_2, aes(x = week, y = state, fill = total_polls)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey90") +
  labs(x = "Week",
       y = "State",
       fill = "Total Polls") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), strip.text = element_text(size = 8))

@@

```{r}
#| label: fig-correlation2
#| fig-cap: "Polling concentration over time by pollster (*Note:* Concentrated polling efforts of Siena/NYT are shown in the first half of September, 2024.)"
#| echo: false
#| fig-align: center
#| page-break-after: true

@@

# Plot a heatmap of polling activity by state and week
ggplot(poll_time_pollster, aes(x = week, y = pollster, fill = total_polls)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey90") +
  labs(x = "Week",
       y = "Pollster",
       fill = "Total Polls") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), strip.text = element_text(size = 8))

@@

```{r}
#| label: fig-correlation3
#| fig-cap: "Polling activity by pollster and state (*Note:* Siena/NYT has strongest state-level polling coverage in key battleground states)"
#| echo: false
#| page-break-after: true

@@

# Step 2: Plot the faceted map using plot_usmap
plot_usmap(data = pollster_state_data, values = "total_polls", regions = "states") +
  facet_wrap(~ pollster, ncol = 4) +  # Create a map for each pollster
  scale_fill_distiller(palette = "Blues", direction = 1, na.value = "gray90") +  # Use blue color palette
  labs(fill = "Total Polls") +
  theme_void() +  # Remove axes and gridlines
  theme(strip.text = element_text(size = 9))  # Customize facet labels

@@

Our modelling strategy estimates Kamala Harris's support percentage in the 2024 US election polls, accounting for potential variations over time including pollster and state differences. The model balances complexity with interpretability, using both linear and Bayesian frameworks to capture patterns in the data. We turned from the initial linear model to a Bayesian model for robust predictions considering the variables' uncertainties. The Bayesian approach, which incorporates both prior beliefs and observed data to make predictions, allowed us to capture the variances among pollsters and states more accurately and responsively. Further background details and diagnostics are included in [Appendix -@sec-model-details].

@@

## Results from examining the analysis data

@@

```{r}
#| label: fig-resultplot1
#| fig-cap: "Polling votes for Harris over time (*Note:* The date starts from after Harris officially announced her campaign for 2024 U.S. presidential election on July 21, 2024.)"
#| echo: false
#| warning: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

@@

When accounting for the pollster difference, @fig-resultplot2 and @fig-resultplot3 show variations in Harris' support levels that are obscured in the aggregated view of @fig-resultplot1. Siena/NYT (pink) shows relatively stable polling results for Harris, with fewer extreme values and a slight downward trend in October. On the other hand, Emerson (green) shows more fluctuation throughout the period with a wider spread of polling values.

```{r}
#| label: fig-resultplot2
#| fig-cap: "Polling votes for Harris over time by pollster (*Note:* The date starts from after Harris officially announced her campaign for 2024 U.S. presidential election on July 21, 2024. Only filtered pollsters with high-quality polling questions are shown in the following.)"
#| echo: false
#| warning: false
#| message: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

@@

```{r}
#| label: fig-resultplot3
#| fig-cap: "Polling votes for Harris over time by pollster (facets) (*Note:* The date starts from after Harris officially announced her campaign for 2024 U.S. presidential election on July 21, 2024. Only filtered pollsters with high-quality polling questions are shown in the following.)"
#| echo: false
#| warning: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

@@

```{r}
#| label: fig-resultplot4
#| fig-cap: "Polling votes for Harris over time by state (*Note:* The date starts from after Harris officially announced her campaign for 2024 U.S. presidential election on July 21, 2024. Only filtered pollsters with high-quality polling questions are shown in the following.)"
#| echo: false
#| warning: false
#| message: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

# Color by pollster
base_plot +
  geom_point(aes(color = state)) +
  geom_smooth() + 
  theme(legend.position = "bottom")
```

```{r}
#| label: fig-resultplot5
#| fig-cap: "Polling votes for Harris over time by state (facets) *Note:* The date starts from after Harris officially announced her campaign for 2024 U.S. presidential election on July 21, 2024. Only filtered pollsters with high-quality polling questions are shown in the following."
#| echo: false
#| warning: false
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

@@

Prediction results derived from our model frameworks are summarized in @tbl-modelresults1 and @tbl-modelresults2. In the linear models (@tbl-modelresults1), higher $R^2$ and lower WAIC, RMSE values in the second column show that the inclusion of pollster effects improves accuracy and reliability of the prediction model. In the Bayesian models (@tbl-modelresults2), higher Log-Likelihood and lower ELPD, WAIC values in the fourth column shows that including both pollster and state effects enhances model performance.

\

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults1
#| tbl-cap: "Linear models of support percentages for Harris based on date and pollster"
#| warning: false
#| tbl-width: 80% 
#| page-break-after: true
#| page-break-before: true

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults2
#| tbl-cap: "Bayesian models of support percentages for Harris based on pollster and state"
#| warning: false
#| tbl-align: center
#| tbl-width: 80% 
#| page-break-after: true
#| page-break-before: true

@@

While our model provides a foundation to understand Harris' polling support, further refinements are necessary to enhance its accuracy and applicability. For instance, future studies could focus on the incorporation of voter demographics, such as age, gender, and education. Showing which segments of the population are driving changes in support, this can give further explanation to how certain policies or campaign events of candidates affect overall support for a candidate [@brown2024candidate]. In addition, interaction terms between pollster and state can be included in the model, considering that some states might receive disproportionately more attention from certain pollsters as shown in @fig-correlation3. This can give further explanation to how pollsters and regional dynamics affect overall support for a candidate [@pew2020electionpolls].

This study has its constraints in that sampling error and systematic biases inevitably occur in the process of measuring social phenomenon with data. In particular, due to the nature of polling surveys, non-responses or misunderstanding of the survey questions result in missing data or outliers [@pew2020electionpolls]. Considering the possibility of prediction errors, we should take caution in interpreting the analysis and prediction results. By conducting more in-depth research of the domain knowledge and constructing appropriate variables to put into account, it would help derive accurate conclusions rather than just acknowledging the numbers given itself [@geeksforgeeks2023domainknowledge].

@@

# Appendix {#sec-appendix}

## Pollster methodology overview and evaluation

@@

## Idealized methodolgy

@@

### Idealized survey

The proposed survey questionnarie design is in the following link:
\
https://forms.gle/zQ8iJyPk3HhJYrKd9.

::: {.layout}
### Survey demo

@@

## Model details {#sec-model-details}

### Posterior predictive check

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheck
#| layout-ncol: 2
#| fig-cap: "Examining how the Bayesian model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check"]
#| fig-align: center
#| fig-width: 5
#| page-break-after: true

@@

### Diagnostics

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2
#| fig-align: center
#| fig-width: 5
#| page-break-after: true
